---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

This vignette will walk you through the process of using this R package to update an attribute on Exist.io.

# Setup

The first step is to create an API client on Exist.io. There you have to enter a name for your API and client and provide a redirect URI. To be able to use this R package you have to provide this URI: https://localhost:1410/.

Once you have created your API client you will be provided with a client id and a client secret. Store these as environment variables. You can do so in your .Renviron or set these using the following lines.

```{r enviroment}
# Set environment variables
Sys.setenv(EXIST_CLIENT_ID = "PASTE_YOUR_ID_HERE")
Sys.setenv(EXIST_CLIENT_SECRET = "PASTE_YOUR_SECRET_HERE")
```

After you set these environment variables you can get started using the package. For this load the package and then authenticate to Exist.io.

```{r auth}
# Load package
library(existR)

# Authenticate to Exist.io
exist_auth()
```

Calling the exist_auth function will open a browser window. You will have to sign into Exist.io and then grant access to the R package. Afterwards you will be redirect. However, the redirect URL needs to be changed. Exist.io requires a https redirect URL, but the httr package can only provide a local webserver with http. Therefore, to finish the authentication process you have to change the URL in your browser. Just remove the s in https and the URL will work. This will lead to a file being saved in your working directory that contains your OAuth token.

# Attribute ownership

Before an attribute can be updated you have to acquire ownership of this attribute. You can so as shown in the following example.

```{r ownership}
# Acquire ownership of the 'money_spent' attribute.
exist_acquire_attribute("money_spent")
```

# Update an attribute

Once ownership of an attribute has been acquired the attribute can updated. In the following example I will update the money_spent attribute for the 30th of January 2020 to the value of 16.

```{r update}
# Update the attribute
exist_update_attribute("money_spent", "2020-01-30", 16)
```